### 2015-11-28 config/glossaries.inc.tex
Patching up some references

\newacronym{CRLB}{CRLB}{Cramér-Rao Lower Bound}
\newacronym{CZT}{CZT}{Chirp $Z$ Transform}

\newacronym{DC}{DC}{direct current}
\newacronym{DFT}{DFT}{Discrete Fourier Transform}
\newacronym{DSA}{DSA}{dynamic signal analyzer}
\newacronym{DUT}{DUT}{device under test}

@@

\newacronym{FFT}{FFT}{Fast Fourier Transform}
\newacronym{FRF}{FRF}{frequency response function}

@@

\newacronym{MIMO}{MIMO}{multiple-input Multiple Output}
\newacronym{MISO}{MISO}{Multiple Input Single Output}
\newacronym{MSE}{MSE}{mean squared error}

@@

\newacronym{SIMO}{SIMO}{Single Input Multiple Output}
\newacronym{SISO}{SISO}{single-input single-output}
\newacronym{SPICE}{SPICE}{Simulation Program with Integrated Circuit Emphasis}
\newacronym{SNR}{SNR}{signal to noise ratio}

>>>>

\newacronym{CRLB}{CRLB}{Cramér-Rao lower bound}
\newacronym{CZT}{CZT}{chirp $Z$-transform}

\newacronym{DC}{DC}{direct current}
\newacronym{DFT}{DFT}{discrete Fourier transform}
\newacronym{DSA}{DSA}{dynamic signal analyzer}
\newacronym{DTFT}{DFT}{discrete-time Fourier transform}
\newacronym{DUT}{DUT}{device under test}

@@

\newacronym{FFT}{FFT}{fast Fourier transform}
\newacronym{FRF}{FRF}{frequency response function}

@@

\newacronym{MIMO}{MIMO}{multiple-input multiple-output}
\newacronym{MISO}{MISO}{multiple-input single-output}
\newacronym{MSE}{MSE}{mean squared error}

\newacronym{OE}{OE}{output-error}

@@

\newacronym{SIMO}{SIMO}{single-input multiple-output}
\newacronym{SISO}{SISO}{single-input single-output}
\newacronym{SPICE}{SPICE}{Simulation Program with Integrated Circuit Emphasis}
\newacronym{SNR}{SNR}{signal to noise ratio}
